---
title: "First lesson."
author: "John Park"
date: "July 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rcrossref)
library(jsonlite)
```

## Get metadata from journal 

This is the first tutorial about using crossref API for getting text data from literatures. CrossRef API <https://github.com/CrossRef/rest-api-doc>.


```{r}
## example of work retrieving from jouranl 'landscape ecology'
all.lands.ecol<-cr_works(filter=c(issn='15729761-09212973'))
all.lands.ecol.json<-fromJSON(all.lands.ecol)
```
using crossref api: the command is,
https://api.crossref.org/works?facet=license:*&filter=issn:15729761-09212973

result is the same for crossref api and rcrossref. 

I have digged this for an hour, but not sure how to list the data in this format I want:

id |title | year | citation 

the result

```{r}
all.lands.ecol$data$title
```

Only gives the title of 20 article, whereas 

```{r}
all.lands.ecol$meta
```

Gives total search results of 2374 journals. It must have something to do with items_per_page entry, which is 20. I just need to figure out how to fetch the data, I guess.

