---
title: "First lesson."
author: "John Park"
date: "July 11, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rcrossref)
library(jsonlite)
library(dplyr)
library(parallel)
```

## Get metadata from journal 

This is the first tutorial about using crossref API for getting text data from literatures. CrossRef API <https://github.com/CrossRef/rest-api-doc>.


```{r}
## example of work retrieving from jouranl 'landscape ecology'
issn.target='15729761-09212973'
DownPubs=cr_works(filter=c(issn=issn.target))

```
using crossref api: the command is,
https://api.crossref.org/works?facet=license:*&filter=issn:15729761-09212973

result is the same for crossref api and rcrossref. 

Since cr_works only takes first 20 data points, set offset and do recurrent download based on the total number of publications found in the journal.  
```{r}
n_pages <- ceiling(DownPubs$meta$total_results / DownPubs$meta$items_per_page)
myfunc<-function(x){ n_line <- (x - 1)*20 + 1;
return( cr_works(filter = c(issn=issn.target), offset = n_line)$data )
}
ls.pubs<-c(1:n_pages)%>%lapply(.,FUN=myfunc)
  
for (i in 1:n_pages){
  if(is.null(ls.pubs[[i]])==FALSE){
  ls.pubs[[i]]<-ls.pubs[[i]]%>%select(title,author,issued)
  }
}
ls.pubs<-do.call("rbind",ls.pubs)
ls.pubs
```

Need slam, slam needs R>3.4.0

```{r}
pubs_title<-paste(ls.pubs$title, collapse = " ")
s<-as.String(pubs_title)
sent_token_annotator<-Maxent_Sent_Token_Annotator()
word_token_annotator<-Maxent_Word_Token_Annotator()
a<-annotate(s,list(sent_token_annotator,word_token_annotator))

```